Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-04 paper.tex
Reduced all table sizes to fix in the page. Slighty related with the closed issue #24 :P

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, P. de las Cuevas$^1$, M.G. Arenas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
  jmerelo@geneura.ugr.es, pgarcia@geneura.ugr.es,
  antares.es@gmail.com, palomacd@ugr.es, mgarenas@ugr.es}
}
% Antonio - Hossam add your 'official' e-mail here. ;)

@@

\begin{table}
\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
\hline 
RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline 
\end{tabular}

% CFSSUBEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
\hline 
K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
\end{tabular}\\

% SOM
\centering{}% SOM
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
\hline 
K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
\hline 
RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
\hline 
LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
\hline 
SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Description of publishing companies considered as special cases.
\label{tab:desc_publishing companies}}
\centering{}%
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling publishing company\\
\hline 
\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
\label{Table:special_cases}
\end{table}

@@

\begin{table}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
\hline 
K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
\hline 
RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results-RAE}
\end{table}

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, P. de las Cuevas$^1$, M.G. Arenas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
  jmerelo@geneura.ugr.es, pablogarcia@ugr.es,
  antares.es@gmail.com, palomacd@ugr.es, mgarenas@ugr.es}
}
% Antonio - Hossam add your 'official' e-mail here. ;)

@@

\begin{table}
\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
\hline 
RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline 
\end{tabular}
}
% CFSSUBEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
\hline 
K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
\end{tabular}
}
% SOM
\centering{}% SOM
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
\hline 
K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
\hline 
RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
\hline 
LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
\hline 
SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}
\caption{Description of publishing companies considered as special cases.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling publishing company\\
\hline 
\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
}
\label{Table:special_cases}
\end{table}

@@

\begin{table}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case4results}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
\hline 
K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case1results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
\hline 
RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case2results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS) }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case3results-RAE}
\end{table}
